An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/motiv.tex
better motiv

We call the above situation a {\em fine-grained value correlation
error}, which is a more challenging case than 
{\em value correlation error} reported
by some existing investigations~\cite{yin11anempirical, zhang14encore}.
A typical value correlation error
means one entry's value should have a certain correlation with
another entry's value. For example, in MySQL,
the value of {\tt max\_connections} should be higher than
{\tt mysql.max\_persistent}. Although some work, \eg,
EnCore~\cite{zhang14encore}, can detect the normal value
correlation case, 
no existing effort can detect fine-grained value correlation
errors, which ``hides'' an equation-aware correlation, as shown in
the above example.
As mentioned by Xu {\em et al.}~\cite{xu15hey},
detecting fine-grained value correlation errors 
is a much more challenging
task than the normal value correlation problems.

To the best of our knowledge, \app is the first effort that
is able to check such fine-grained value correlation problem.
If we run \app on this configuration file, \app  would return:

@@

Note that existing effort, EnCore, aims to detect value correlation 
errors. However, different from \app, EnCore can only detect simple
correlation, \eg, {\tt mysql.max\_persistent} < {\tt max\_connections},
rather than the fine-grained computation-based value correlation,
like {\tt key\_buffer\_size >= max\_connections * sort\_buffer\_size}
identified by \app.

\para{Example~3: Entry missing errors.} 
Many critical system outages result from the fact that important
entry was missing in the configuration file. 
We call such a problem as {\em entry missing error}.
In a public misconfiguration dataset~\cite{configdataset},
the major problems of MySQL failure reports were caused by
entry missing errors.
Below is a real-world entry missing error example~\cite{yin11anempirical},
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
done through the following entries in the OpenLDAP configuration file:

>>>>

We call the above situation a {\em fine-grained value correlation
error}, which is a more challenging case than 
{\em value correlation error} reported
by some existing investigations~\cite{yin11anempirical, zhang14encore}.
A typical value correlation error
means one entry's value should have a certain correlation with
another entry's value. For example, in MySQL,
the value of {\tt max\_connections} should be higher than
{\tt mysql.max\_persistent}. Although some work, \eg,
EnCore~\cite{zhang14encore}, can detect the normal value
correlation case, 
no existing effort can detect fine-grained value correlation
errors, which ``hide'' equation-aware correlations, as shown in
the above example.
As mentioned by Xu {\em et al.}~\cite{xu15hey},
detecting fine-grained value correlation errors 
is a much more challenging
task than the normal value correlation problem.

To the best of our knowledge, \app is the first effort that
is able to check such fine-grained value correlation problems.
If we run \app on this configuration file, \app  would return:

@@

\jon{The following paragraph is repetitive, same as the one two above -- just remove it?}
Note that an existing effort, EnCore, aims to detect value correlation 
errors. However, different from \app, EnCore can only detect simple
correlations, \eg, {\tt mysql.max\_persistent} < {\tt max\_connections},
rather than the fine-grained computation-based value correlation,
like {\tt key\_buffer\_size >= max\_connections * sort\_buffer\_size}
identified by \app.

\para{Example~3: Entry missing errors.} 
Many critical system outages result from the fact that an important
entry was missing in the configuration file. 
We call such a problem as {\em entry missing error}.
In a public misconfiguration dataset~\cite{configdataset},
many MySQL failure reports were caused by
entry missing errors.
Below is a real-world entry missing error example~\cite{yin11anempirical},
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
done through the following entries in the OpenLDAP configuration file:
